My title

### 2024-11-26 paper/paper.qmd
update plots

Our results are summarized in @tbl-modelresults.

``````{r}
#| echo: false
#| eval: true
#| warning: false
#| message: false
#| label: fig-coefficient
#| fig-cap: Income Distribution for Unmarried Individuals

@@

# Create the coefficient plot
ggplot(model_summary, aes(x = term, y = estimate, ymin = conf.low, ymax = conf.high)) +
  geom_pointrange(color = "orange") +
  geom_hline(yintercept = 0, linetype = "dashed") +
  coord_flip() +
  labs(
    title = "Coefficients and Confidence Intervals from Logistic Regression",
    x = "Predictors",
    y = "Coefficient Value"
  ) +
  theme_minimal()
```

@@

# Create the age distribution plot
ggplot(unmarried_data, aes(x = age)) +
  geom_histogram(aes(y = ..density..), bins = 30, fill = "salmon", color = "black", alpha = 0.7) +
  geom_density(color = "red", size = 1) +
  ggtitle("Age Distribution for Unmarried Individuals") +
  xlab("Age") +
  ylab("Density") +
  theme_minimal()
```

# Discussion

>>>>

```{r}
#| echo: false
#| eval: true
#| warning: false
#| message: false
#| label: fig-coefficient
#| fig-cap: Income Distribution for Unmarried Individuals

@@

# Create the coefficient plot
ggplot(model_summary, aes(x = term, y = estimate, ymin = conf.low, ymax = conf.high)) +
  geom_pointrange(color = "orange") +
  geom_hline(yintercept = 0, linetype = "dashed") +
  coord_flip() +
  labs(
    title = "Coefficients and Confidence Intervals",
    x = "Predictors",
    y = "Coefficient Value"
  ) +
  theme_minimal()
```

@@

# Create the age distribution plot
ggplot(unmarried_data, aes(x = age)) +
  geom_histogram(aes(y = ..density..), bins = 30, fill = "salmon", color = "black", alpha = 0.7) +
  geom_density(color = "red", size = 1) +
  ggtitle("Age Distribution for Unmarried Individuals") +
  xlab("Age") +
  ylab("Density") +
  theme_minimal()
```
```{r}
#| echo: false
#| eval: true
#| warning: false
#| message: false
#| label: fig-edu-marriage
#| fig-cap: Proportions of Marital Status by Education Level
#| 
# Calculate proportions of marital status within each education level
education_marital_status <- data %>%
  group_by(education_level, marital_status) %>%
  summarise(count = n()) %>%
  ungroup() %>%
  group_by(education_level) %>%
  mutate(proportion = count / sum(count))

# Create the stacked bar chart with percentages and orange/blue colors
ggplot(education_marital_status, aes(x = education_level, y = proportion, fill = marital_status)) +
  geom_bar(stat = "identity", position = "stack") +
  geom_text(
    aes(label = scales::percent(proportion, accuracy = 1)),
    position = position_stack(vjust = 0.5), size = 3.5, color = "white"
  ) +
  scale_fill_manual(values = c("Not_Married" = "#FFA500", "Married" = "#4682B4")) +
  labs(
    title = "Proportions of Marital Status by Education Level",
    x = "Education Level",
    y = "Proportion",
    fill = "Marital Status"
  ) +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```
```{r}
#| echo: false
#| eval: true
#| warning: false
#| message: false
#| label: fig-race-marriage
#| fig-cap: Proportions of Marital Status by Race

# Calculate proportions of marital status within each race
race_marital_status <- data %>%
  group_by(Race, marital_status) %>%
  summarise(count = n()) %>%
  ungroup() %>%
  group_by(Race) %>%
  mutate(proportion = count / sum(count))

# Create the stacked bar chart with annotations
ggplot(race_marital_status, aes(x = Race, y = proportion, fill = marital_status)) +
  geom_bar(stat = "identity", position = "stack") +
  geom_text(
    aes(label = scales::percent(proportion, accuracy = 1)),
    position = position_stack(vjust = 0.5), size = 3.5, color = "white"
  ) +
  scale_fill_manual(values = c("Not_Married" = "red", "Married" = "blue")) +
  labs(
    title = "Proportions of Marital Status by Race",
    x = "Race",
    y = "Proportion",
    fill = "Marital Status"
  ) +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```
```{r}
#| echo: false
#| eval: true
#| warning: false
#| message: false
#| label: fig-gender-marriage
#| fig-cap: Marital Status Proportions by Gender

# Calculate proportions of marital status within each gender
gender_marital_status <- data %>%
  group_by(gender, marital_status) %>%
  summarise(count = n()) %>%
  ungroup() %>%
  group_by(gender) %>%
  mutate(
    proportion = count / sum(count),
    percentage_label = paste0(scales::percent(proportion, accuracy = 1))
  )

# Separate pie charts for each gender with percentage labels
ggplot(gender_marital_status, aes(x = "", y = proportion, fill = marital_status)) +
  geom_bar(stat = "identity", width = 1) +
  geom_text(
    aes(label = percentage_label),
    position = position_stack(vjust = 0.5), size = 4, color = "white"
  ) +
  coord_polar("y", start = 0) +
  facet_wrap(~gender) +
  scale_fill_manual(values = c("Not_Married" = "#FF9999", "Married" = "#66B3FF")) +
  labs(
    title = "Marital Status Proportions by Gender",
    x = NULL,
    y = NULL,
    fill = "Marital Status"
  ) +
  theme_void() +
  theme(
    plot.title = element_text(hjust = 0.5, size = 16),
    strip.text = element_text(size = 14),
    legend.title = element_text(size = 12),
    legend.text = element_text(size = 10)
  )
```
# Discussion
